Smoking and COVID Living Review (v10): a bayesian analysis

### 2021-02-07 reports/bayesian_report.Rmd
completed manuscript

## Table 1: Included studies
``` {r table_1}
#Updating table 1
table_1_word <- table_1 %>%
  mutate(., current_percentage = current_smoker/total*100,
         former_percentage = former_smoker/total*100,
         current_former_percentage = current_former_smoker/total*100,
         never_smoker_percentage = never_smoker/total*100,
         never_smoker_unknown_percentage = never_smoker_unknown/total*100,
         not_stated_percentage = not_stated/total*100,
         missing_percentage = missing/total*100) %>%
  select(lead_author, date_published, country, sample_size, median_age, iqr_lower, iqr_upper, mean_age, lower_range,
         upper_range, standard_deviation, female_sex_percent, current_percentage, former_percentage, current_former_percentage,
         never_smoker_percentage, never_smoker_unknown_percentage, not_stated_percentage, missing_percentage, study_id) %>%
  replace_na(., list(not_stated_percentage = 0, missing_percentage = 0)) %>%
  mutate(., missing_percentage = not_stated_percentage + missing_percentage,
         missing_percentage = formatC(missing_percentage, digits = 2, format = "f"))

@@

a <- a %>%
  select(study_id, lead_author, date_published, country, sample_size, study_setting, median_mean, mean_used, iqr,
         female_sex_percent, current_percentage, former_percentage, current_former_percentage, never_smoker_percentage,
         never_smoker_unknown_percentage, missing_percentage, study_quality_final) %>%
  mutate(median_mean = paste(median_mean, mean_used, sep = ''),
         median_mean = na_if(median_mean, NA)) %>%
  select(-mean_used) %>%
  mutate(median_mean = ifelse(median_mean == 'NA', 'NA', paste(paste(median_mean, iqr, sep = ' ('),')', sep = ''))) %>%
  select(-iqr) %>%
  rename('Study ID' = study_id,
         'Lead author' = lead_author,
         'Date published' = date_published,
         'Country' = country,
         'Sample size' = sample_size,
         'Study setting' = study_setting,
         'Median (IQR)' = median_mean,
         'Female %' = female_sex_percent,
         'Current smoker %' = current_percentage,
         'Former smokers %' = former_percentage,
         'Current/former smokers %' = current_former_percentage,
         'Never smokers %' = never_smoker_percentage,
         'Never/unknown smokers %' = never_smoker_unknown_percentage,
         'Missing %' = missing_percentage,
         "Study quality" = study_quality_final)

@@

saveRDS(a, file = here("data_clean", "table_1_refs.rds"))
source(here("scripts", "references_in_table.r"))
```
The total number of included studies is `r paste(nrow(table_1_word))`. This table is searchable
```{r}
datatable(a) %>%
  formatRound(
    columns = c(8:14),
    digits = 2,
    interval = 3,
    mark = ",",
    dec.mark = getOption("OutDec")
)

@@

a$Author <- to_upper_camel_case(a$Author, sep_out = ", ")
a$Author  <- a$Author  %>%
  recode("Bello, Chavolla" = "Bello-Chavolla",
         "De, Lusignan" = "de Lusignan",
         "Del, Valle" = "del Valle")

numeric_columns <- c('Population_tested', 'SARS_CoV_2_negative', 'N_current_smoker', 'N_former_smoker',
                     'N_current_former_smoker', 'N_never_smoker', 'N_not_stated', 'SARS_CoV_2_positive', 'P_current_smoker',
                     'P_former_smoker', 'P_current_former_smoker', 'P_never_smoker', 'P_not_stated')
a <- flextable(a) %>%
    set_caption(caption = 'SARS-CoV-2 infection by smoking status') %>%
  colformat_double(j = numeric_columns, digits = 0, na_str = '-', big.mark = ',')
```
The number of studies reporting on infection by smoking status is: `r paste(nrow(table_2_word))`
``` {r}
a <- set_header_labels(a,
                       Population_tested = 'Total population tested',
                       SARS_CoV_2_negative = "N (%)",
                       N_current_smoker = "Current smoker (%)",
                       N_former_smoker = "Former smoker (%)",
                       N_current_former_smoker = "Current/former smoker (%)",
                       N_never_smoker = "Never smoker (%)",
                       N_not_stated = "Not stated (%)",
                       SARS_CoV_2_positive = "N (%)",
                       P_current_smoker = "Current smoker (%)",
                       P_former_smoker = "Former smoker (%)",
                       P_current_former_smoker = "Current/former smoker (%)",
                       P_never_smoker = "Never smoker (%)",
                       P_not_stated = "Not stated (%)") %>%
  add_header_row(top = TRUE, values = c("","SARS-CoV-2 negative", "SARS-CoV-2 positive" ), colwidths = c(2, 6, 6)) %>%
  theme_booktabs() %>%
  fix_border_issues() %>%
  set_table_properties(width = 1, layout = 'autofit')  %>%
  colformat_char(na_str = '-')
a

@@

good_quality_2 <- quality_table_2 %>%
  filter(overall_quality != 'good')

fair_quality_2 <- quality_table_2 %>%
  filter(overall_quality != 'fair')

@@

a <- flextable(a) %>%
    set_caption(caption = 'COVID-19 hospitalisation by smoking status') %>%
  colformat_double(j = numeric_columns, digits = 0, na_str = '-', big.mark = ',') %>%
  colformat_char(na_str = '-')

@@

a <- flextable(a) %>%
    set_caption(caption = 'COVID-19 severity by smoking status') %>%
  colformat_double(j = numeric_columns, digits = 0, na_str = '-', big.mark = ',') %>%
  colformat_char(na_str = '-')

@@

a <- flextable(a) %>%
    set_caption(caption = 'COVID-19 mortality by smoking status') %>%
  colformat_double(j = numeric_columns, digits = 0, na_str = '-', big.mark = ',') %>%
  colformat_char(na_str = '-')

>>>>

## Table 1: Included studies
``` {r table_1}
#table 1 for references
table_1_refs <- table_1 %>%
  left_join(., data_study_general %>%
              select(lead_author, doi),
            by = "lead_author")
#Updating table 1
table_1_word <- table_1 %>%
  mutate(., current_percentage = current_smoker/total*100,
         former_percentage = former_smoker/total*100,
         current_former_percentage = current_former_smoker/total*100,
         never_smoker_percentage = never_smoker/total*100,
         never_smoker_unknown_percentage = never_smoker_unknown/total*100,
         not_stated_percentage = not_stated/total*100,
         missing_percentage = missing/total*100) %>%
  select(lead_author, date_published, country, sample_size, median_age, iqr_lower, iqr_upper, mean_age, lower_range,
         upper_range, standard_deviation, female_sex_percent, current_percentage, former_percentage, current_former_percentage,
         never_smoker_percentage, never_smoker_unknown_percentage, not_stated_percentage, missing_percentage, study_id) %>%
  replace_na(., list(not_stated_percentage = 0, missing_percentage = 0)) %>%
  mutate(., missing_percentage = not_stated_percentage + missing_percentage,
         missing_percentage = formatC(missing_percentage, digits = 2, format = "f"))

@@

a <- a %>%
  select(study_id, lead_author, date_published, country, sample_size, study_setting, median_mean, mean_used, iqr,
         female_sex_percent, current_percentage, former_percentage, current_former_percentage, never_smoker_percentage,
         never_smoker_unknown_percentage, missing_percentage, study_quality_final) %>%
  mutate(median_mean = paste(median_mean, mean_used, sep = ''),
         median_mean = na_if(median_mean, NA)) %>%
  select(-mean_used) %>%
  mutate(median_mean = ifelse(median_mean == 'NA', 'NA', paste(paste(median_mean, iqr, sep = ' ('),')', sep = ''))) %>%
  select(-iqr) %>%
  left_join(., table_1_refs %>%
              select(lead_author, doi),
            by = "lead_author") %>%
  rename('Study ID' = study_id,
         'Lead author' = lead_author,
         'Date published' = date_published,
         'Country' = country,
         'Sample size' = sample_size,
         'Study setting' = study_setting,
         'Median (IQR)' = median_mean,
         'Female %' = female_sex_percent,
         'Current smoker %' = current_percentage,
         'Former smokers %' = former_percentage,
         'Current/former smokers %' = current_former_percentage,
         'Never smokers %' = never_smoker_percentage,
         'Never/unknown smokers %' = never_smoker_unknown_percentage,
         'Missing %' = missing_percentage,
         "Study quality" = study_quality_final)

@@

saveRDS(a %>%
          select(doi, everything()) %>%
          select(-"Study ID") %>%
          rename("ref" = doi),
        file = here("data_clean", "table_1_refs.rds"))
#source(here("scripts", "references_in_table.r"))
```
The total number of included studies is `r paste(nrow(table_1_word))`. This table is searchable
```{r}
datatable(a) %>%
  formatRound(
    columns = c(8:14),
    digits = 2,
    interval = 3,
    mark = ",",
    dec.mark = getOption("OutDec")
)

@@

a$Author <- to_upper_camel_case(a$Author, sep_out = ", ")
a$Author  <- a$Author  %>%
  recode("Bello, Chavolla" = "Bello-Chavolla",
         "De, Lusignan" = "de Lusignan",
         "Del, Valle" = "del Valle")
a$Author <- to_upper_camel_case(a$`Lead author`, sep_out = ", ")
author_list <- plyr::mapvalues(a$Author,
                               from = cleaned_names,
                               to = correct_names)

a$Author <- author_list

numeric_columns <- c('Population_tested', 'SARS_CoV_2_negative', 'N_current_smoker', 'N_former_smoker',
                     'N_current_former_smoker', 'N_never_smoker', 'N_not_stated', 'SARS_CoV_2_positive', 'P_current_smoker',
                     'P_former_smoker', 'P_current_former_smoker', 'P_never_smoker', 'P_not_stated')
a <- flextable(a) %>%
    colformat_double(j = numeric_columns, digits = 0, na_str = '-', big.mark = ',')
```
The number of studies reporting on infection by smoking status is: `r paste(nrow(table_2_word))`
``` {r}
a <- set_header_labels(a,
                       Population_tested = 'Total population tested',
                       SARS_CoV_2_negative = "N (%)",
                       N_current_smoker = "Current smoker (%)",
                       N_former_smoker = "Former smoker (%)",
                       N_current_former_smoker = "Current/former smoker (%)",
                       N_never_smoker = "Never smoker (%)",
                       N_not_stated = "Not stated (%)",
                       SARS_CoV_2_positive = "N (%)",
                       P_current_smoker = "Current smoker (%)",
                       P_former_smoker = "Former smoker (%)",
                       P_current_former_smoker = "Current/former smoker (%)",
                       P_never_smoker = "Never smoker (%)",
                       P_not_stated = "Not stated (%)") %>%
  add_header_row(top = TRUE, values = c("","SARS-CoV-2 negative", "SARS-CoV-2 positive" ), colwidths = c(2, 6, 6)) %>%
  theme_booktabs() %>%
  fix_border_issues() %>%
  set_table_properties(width = 1, layout = 'autofit')  %>%
  colformat_char(na_str = '-')
a

@@

good_quality_2 <- quality_table_2 %>%
  filter(overall_quality == 'good')

fair_quality_2 <- quality_table_2 %>%
  filter(overall_quality == 'fair')

@@

a <- flextable(a) %>%
  colformat_double(j = numeric_columns, digits = 0, na_str = '-', big.mark = ',') %>%
  colformat_char(na_str = '-')

@@

a <- flextable(a) %>%
  colformat_double(j = numeric_columns, digits = 0, na_str = '-', big.mark = ',') %>%
  colformat_char(na_str = '-')

@@

a <- flextable(a) %>%
  colformat_double(j = numeric_columns, digits = 0, na_str = '-', big.mark = ',') %>%
  colformat_char(na_str = '-')
